\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-22 paper.qmd
Need to fix later

```{r}
#| echo: false
#| fig-cap: "Model in $2\\text{-}D$, on the tSNE layout, and three views of the fit in projections from $9\text{-}D$, for the PBMC3k data ($(s_1, \ s_2) = (-0.050, \ -0.058)$, $b = 300 \  (15, \ 20)$, $m = 136$, benchmark value to remove large edges is $0.133$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/5Y1hE4i7N2k>)."
#| label: fig-pbmc2-sc
#| fig-pos: H
#| out-height: 100%
#| eval: true

>>>>

```{r}
#| echo: false
#| fig-cap: "Model in $2\\text{-}D$, on the tSNE layout, and three views of the fit in projections from $9\\text{-}D$, for the PBMC3k data ($(s_1, \ s_2) = (-0.050, \ -0.058)$, $b = 300 \  (15, \ 20)$, $m = 136$, benchmark value to remove large edges is $0.133$). (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/5Y1hE4i7N2k>)."
#| label: fig-pbmc2-sc
#| fig-pos: H
#| out-height: 100%
#| eval: true

### 2024-08-22 paper.tex
Need to fix later

\caption{\label{fig-pbmc2-sc}Model in \(2\text{-}D\), on the tSNE
layout, and three views of the fit in projections from \(9  ext{-}D\),
for the PBMC3k data (\((s_1,  s_2) = (-0.050,  -0.058)\),
\(b = 300   (15,  20)\), \(m = 136\), benchmark value to remove large
edges is \(0.133\)). (The \textbf{langevitour} software is used to view
the data with a tour, and the full video is available at
\url{https://youtu.be/5Y1hE4i7N2k}).}

>>>>

\caption{\label{fig-pbmc2-sc}Model in \(2\text{-}D\), on the tSNE
layout, and three views of the fit in projections from \(9\text{-}D\),
for the PBMC3k data (\((s_1,  s_2) = (-0.050,  -0.058)\),
\(b = 300   (15,  20)\), \(m = 136\), benchmark value to remove large
edges is \(0.133\)). (The \textbf{langevitour} software is used to view
the data with a tour, and the full video is available at
\url{https://youtu.be/5Y1hE4i7N2k}).}
